\pkg{cv}: An \proglang{R} Package for Cross-Validating Regression Models

### 2025-05-11 scratch/JSS-submission/Final_submission/jss5535.tex
fix "the the" typo
add Georges's email

\Address{
    John Fox\\
    McMaster University\\
    Hamilton, Ontario, Canada\\
  E-mail: \email{jfox@mcmaster.ca}\\
  URL: \url{https://www.john-fox.ca/}\\~\\
      Georges Monette\\
    York University\\
    Toronto, Ontario, Canada\\
  E-mail: \email\\
  URL: \url{http://blackwell.math.yorku.ca/gmonette}\\~\\
  }

@@

Figure~\ref{fig:BEPS-plot} shows an ``effect plot,'' using the the
\pkg{effects} package \citep{FoxWeisberg:2019} to visualize the
\code{Europe} \(\times\) \code{political.knowledge} interaction in a
``stacked-area'' graph:

>>>>

\Address{
    John Fox\\
    McMaster University\\
    Hamilton, Ontario, Canada\\
  E-mail: \email{jfox@mcmaster.ca}\\
  URL: \url{https://www.john-fox.ca/}\\~\\
      Georges Monette\\
    York University\\
    Toronto, Ontario, Canada\\
  E-mail: \email{georges@yorku.ca}\\
  URL: \url{http://blackwell.math.yorku.ca/gmonette}\\~\\
  }

@@

Figure~\ref{fig:BEPS-plot} shows an ``effect plot,'' using the
\pkg{effects} package \citep{FoxWeisberg:2019} to visualize the
\code{Europe} \(\times\) \code{political.knowledge} interaction in a
``stacked-area'' graph:
